SOURCE SEPARATION METHODS FOR COMPUTER-ASSISTED ORCHESTRATION

### 2021-06-14 source_separation/paper/paper.tex
Update paper.tex

	 Among the different approaches and techniques of computer-assisted orchestration, one of them, \textit{target-based orchestration}~\cite{Maresz2003}. Target-based computer-assisted orchestration helps composers explore new timbral possibilities by combining instrumental samples in such a way as to mimic the timbre of a given target sound. This target corresponds to an audio extract, of the composer's choice, which can be musical or not. Formally, it is the process of creating an orchestral score that best matches an arbitrary target sound given a similarity metric and constraints.

@@

  For example, consider a target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, even though only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone.

>>>>

	 Among the different approaches and techniques of computer-assisted orchestration, one of them is \textit{target-based orchestration}~\cite{Maresz2003}. Target-based computer-assisted orchestration helps composers explore new timbral possibilities by combining instrumental samples in such a way as to mimic the timbre of a given target sound. This target corresponds to an audio extract, of the composer's choice, which can be musical or not. Formally, it is the process of creating an orchestral score that best matches an arbitrary target sound given a similarity metric and constraints.

@@

  For example, consider a target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also affect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, even though only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone.
